```{r,echo=FALSE,message=FALSE}
source("setup.R")
```

## Start dosing after time = 0

So far, we've always started dosing on the first record of the 
simulation. In model 5, we show how to start dosing at some 
later time, after the simulation has been runing for a while.

We also show you how to turn a bolus dose into an infusion.

- Use the `evtools` plugin
- The dynamic dosing stuff goes in the `[ event ]` block
- Call `evt::bolus()` to create the basic (bolus) dose
- Call `evt::rate()` to set the infusion rate
- Call `evt::ss()` to advance the system to pharmacokinetic steady state
  prior to starting the dose
- Call `evt::ii()` to set the dosing interval
- Call `evt::addl()` to schedule additional doses
- Then `push()` the object back to mrgsolve



The model looks like this:

```{c, eval = FALSE, filename = "model/evtools-5.solv", code = readLines("model/evtools-5.solv")}

```

We've hard-coded the interval and total number of doses for clarity; you
will probably want to make the number of doses and maybe the interval
a parameter so you can change those from simulation to simulation. 

```{r}
mod <- mread("model/evtools-5.solv")

out <- mrgsim(mod, end = 336, delta = 0.25)

plot(out)
```

