```{r,echo=FALSE,message=FALSE}
source("setup.R")
```

## Dose by dose regimen

Previous vignettes showed how to schedule a series of doses into the future. 
This vignette shows a dosing regimen that proceds dose-by-dose. This approach 
is the gateway to doing highly-customized adaptive dosing. 

In this example, we dose by infusion.

- Use the `evtools` plugin
- The dynamic dosing stuff goes in the `[ event ]` block
- Whenever `TIME` matches up with the expected dosing time 
  (based on `INTERVAL`), we trigger a dose.
- Then `push()` the object back to mrgsolve


## Check next dose using `std::fmod()`

```{c, eval = FALSE, filename = "model/evtools-3.solv", code = readLines("model/evtools-3.solv")}

```

```{r}
mod <- mread("model/evtools-3.solv")

out <- mrgsim(mod, end = 120, delta = 0.25)

plot(out)
```

We didn't really specify a dose end time, so the dosing will go as long as we simulate.

```{r}
out <- mrgsim(mod, end = 360, delta = 0.25)

plot(out)
```

## Check next dose using `evt::near()`

In model 4, we have a slightly different mechanism for figuring out when 
the `next` dose should be given - using the `evt::near()` function.


```{c, eval = FALSE, filename = "model/evtools-4.solv", code = readLines("model/evtools-4.solv")}

```

The mechanics should work the same as model 3. 

```{r}
mod <- mread("model/evtools-4.solv")

out <- mrgsim(mod, end = 120, delta = 0.25)

plot(out)
```
