```{r,echo=FALSE,message=FALSE}
source("setup.R")
```

## `mrg::report()`

When debugging model code, it is sometimes helpful to write
print statements at strategic locations to see what is happening
during the model run. 

In this example, we are infusing a dose over 2 hours and want to 
check the concentration at the end of the infusion. For simplicity, 
we'll just print that value to the console. 

```{c, eval = FALSE, filename = "model/mrg-report-1.solv", code = readLines("model/mrg-report-1.solv")}

```

```{r}
mod <- mread("model/mrg-report-1.solv")
```

```{r}
dose <- ev(amt = 100, tinf = 4)

out <- mrgsim(mod, dose)
```

```{r, echo = FALSE}
cat("from report 1.38852")
```


The obvious downside to this approach is you can easily flood the console with 
outputs that are hard to make sense of. In that case, you can use a more 
controlled approach, saving each value you eventually want reported and 
then assigning those objects into the model environment. An example is shown
here. 

```{c, eval = FALSE, filename = "model/mrg-report-2.solv", code = readLines("model/mrg-report-2.solv")}

```


```{r}
mod <- mread("model/mrg-report-2.solv")

dose <- mutate(dose, ii = 24, addl = 3)

out <- mrgsim(mod, dose, end = 240, delta = 0.1)

out <- mutate_sims(out, CP = A1/mod$V)

plot(out, CP ~ time)
```

To pull the data from the model environment, you run:
```{r}
env_get(mod, "eof")
```
