```{r,echo=FALSE,message=FALSE}
source("setup.R")
```

## `mrgx::get()`

### Get from model environment

Every mrgsolve model object contains a R environment where you can maintain 
R objects, typically for use in your model. We will use `mrgx::get()` inside
the model to get access to that object. 


First, let's create a toy model, with an object seeded in the model environment.

```{c, eval = FALSE, filename = "model/mrgx-get-1.solv", code = readLines("model/mrgx-get-1.solv")}

```

```{r}
mod <- mread("model/mrgx-get-1.solv")
```

This object now has a numeric vector named `numbers` in the model environment.

```{r}
env_get(mod, "numbers")
```

Now, let's `get()` that object in a `[ table ]` block.

```{c, eval = FALSE, filename = "model/mrgx-get-2.solv", code = readLines("model/mrgx-get-2.solv")}

```

In this example, we grab a numeric vector from the model environment and 
copy some of the numbers into the simulated output.

```{r}
mod <- mread("model/mrgx-get-2.solv")
```

```{r}
mrgsim(mod, end = 10)
```

You can also update an object in the model environment to a different value
and simulate again.

```{r}
mod <- env_update(mod, numbers = runif(30, 2, 4))

mrgsim(mod)
```

or use `base::assign`:

```{r}
vec <- -rnorm(30, 82, 10)

assign("numbers", envir = env_get_env(mod), vec)

mrgsim(mod)
```


### Get from global environment

You can also get an object from the global environment. 

```{c, eval = FALSE, filename = "model/mrgx-get-3.solv", code = readLines("model/mrgx-get-3.solv")}

```

```{r}
magic_number <- 98765

mod <- mread("model/mrgx-get-3.solv")

mrgsim(mod)
```

Note that this model requires you to have `magic_number` defined in the 
global environment _at run time_. While you _can_ do this, it would be 
_better_ if you defined `magic_number` in the model environment, so the 
definition stays with the model.


### Get from a package

In this example, we `get()` some functions from `base` and assign an 
integer vector back into the global environment.

```{c, eval = FALSE, filename = "model/mrgx-get-4.solv", code = readLines("model/mrgx-get-4.solv")}

```

Check that `indices` doesn't exist.
```{r}
exists("indices")
```

Now load and simulate from the model.

```{r}

mod <- mread("model/mrgx-get-4.solv")

out <- mrgsim(mod)
```

During the model run, we've called `base::seq()` to generate a sequence
of integers, then called `base::assign()` to assign to an `indices` object
in the global environment. 

```{r}
exists("indices")

indices
```

Again, assigning to the global environment probably isn't the safest thing 
to do. We included and environment in the model to give you a safe place
to assign and get R objects during the model run.

