```{r,echo=FALSE,message=FALSE}
source("setup.R")
```

## `mrgx::readRDS()`

You can read an R object from an `.rds` file. To do this, use the templated 
function `mrgx::readRDS()`. This is a templated function because you have to 
specify the type of object coming back from the `.rds` file in the function 
call. 

### DataFrame example

For example, let's take the `mtcars` data frame on a round trip: 

1. Write the data frame to an `.rds` file
2. Compile a model that reads in the data frame from the `.rds` file
3. Assign the data frame object to the model environment
3. Get the object from the model environment

This is obviously a trivial example and normally, you'd _do_ something with 
the object. But hopefully this will clearly illustrate how to use 
`mrgx::readRDS()`.


First, create the file.

```{r}
saveRDS(mtcars, "data/mtcars.rds")
```


Now, we'll use this model to read in the `.rds` file. 

```{c, eval = FALSE, filename = "model/readRDS-1.solv", code = readLines("model/readRDS-1.solv")}

```

Notice that the function call is:

```{c, eval = FALSE}
Rcpp::DataFrame mtc = mrgx::readRDS<Rcpp::DataFrame>("<filename>");
```

We have to not only tell the compiler about the type of object we are assigning
to `mtc`, but we also have to specialize the `mrgx::readRDS()` function, saying
we want a version that returns `Rcpp::DataFrame`. 


```{r}
mod <- mread("model/readRDS-1.solv")
```

Just simulate from the model

```{r}
out <- mrgsim(mod)
```

Now, go into the model object and `get()` the data frame

```{r}
env_get(mod, "data") %>% head()
```

```{r}
#| echo: false
unlink("data/mtcars.rds")
```


### NumericVector example

If the `.rds` file contained a `NumericVector`, you'd have to tell the
compiler that detail like this


```{c, eval = FALSE, filename = "model/readRDS-2.solv", code = readLines("model/readRDS-2.solv")}

```


Now let's round-trip this vector or random numbers

```{r}
set.seed(1234)

x <- rnorm(10)

saveRDS(x, file = "data/random.rds")

mod <- mread("model/readRDS-2.solv")

out <- mrgsim(mod)

env_get(mod, "random")
```

```{r}
#| echo: false
unlink("data/random.rds")
```

### Function example

You could also use this mechanism as a way to call an R function in your model.

This is a function factory, creating a function to do a random draw from a 
fixed `mean` and `sd`.

```{r}
makef <- function(mean, sd) {
  force(mean)
  force(sd)
  function(n) {
    rnorm(n, mean, sd)  
  }
}

saveRDS(object = makef(100, 10), file = "data/draw.rds")
```

Load this model.

```{c, eval = FALSE, filename = "model/readRDS-3.solv", code = readLines("model/readRDS-3.solv")}

```

Here, we get the function from the `.rds` file and call it, asking 
for 1000 replicates using the `mean` and `sd` specified above.


```{r}
mod <- mread("model/readRDS-3.solv")
```

Simulate and get the results. 

```{r}
out <- mrgsim(mod)

x <- env_get(mod, "numbers")

hist(x)
```

Again, these are all just simple examples to show you how you can shuttle R
objects into your mrgsolve model. If you needed this functionality, you'd more 
than likely call the function or work with the object coming from the `.rds` 
file in your model. If you did need to check on what happened, you can always 
`assign()` like we do here to see the object once the simulation ends.

