```{r,echo=FALSE,message=FALSE}
source("setup.R")
```

## `mrgx::assign()`

### Trivial example

The `assign()` function lets you write data generated in the model 
code to the model environment. The arguments follow the order in 
`base::assign()`:

- `"name"` - the name of the object you want to write
- `value` - the value to assign to `name`
- `self` - the model self object

As a trivial example, we sum up `TIME` through the duration of the 
simulation, writing out `cumtime` at every step.

```{mread, stem = "assign-simple", annot = TRUE}
[ plugin ] mrgx

[ error ] 

static local_double cumtime = 0; 
cumtime += TIME;

mrgx::assign("cumtime", cumtime, self);

```

```{r}
mod <- mread("inline/assign-simple.solv")

out <- mrgsim(mod)
```

To get teh value of `cumtime`, use `env_get()`: 
```{r}
env_get(out, "cumtime")
```

The model object holds the environment we are writing to and the output
object contains a copy of the model object. So you can call `env_get()` on 
either the model object (`mod`) or the output object (`out`). If you 
already coerced the simulated output to a data frame, you can always go back
and fetch your assigned data through the model object. In this sense, it is 
probably safer to just always loo in the model object. 

Note, also, that we are writing `cumtime` out at every single data set 
time step, but we only get to see the final value. It would be more efficient
if we only wrote the data once the problem was finished. Read through the 
next example to see how to do this.

### More involved


In this example, we will collect simulation outputs in an object inside 
the model as the simulation progresses. Once the simulation is finished, 
we will (manually) create a data frame of the output and `assign()` it 
into the model environment. 


```{r}
mod <- mread("model/assign.solv")
```

The key part of the code is found below. In `$ERROR`, we will "push" the 
current values of `TIME` and `DV` into the back of the collection 
object. Then, when we detect that we are on the last (final) row of the 
problem, we'll (i) create a data frame with all the data and (ii) 
`assign()` it to the model environment.

```{c, eval = FALSE}
[ error ] 

Time.push_back(TIME);
Dv.push_back(A/V);

if(FINAL_ROW) {
  Rcpp::DataFrame data = Rcpp::DataFrame::create(
    Rcpp::Named("TIME") = Time, 
    Rcpp::Named("DV") = Dv
  );
  mrgx::assign("data", data, self);
}
```



```{c, code = mod@code, eval = FALSE}

```


```{r}
out <- mrgsim(mod, end = -1, add = c(0,240))

out
```


```{r}
data <- env_get(mod, "data")

head(data)

ggplot(data, aes(TIME,DV)) + geom_line()
```
