```{r,echo=FALSE,message=FALSE}
source("setup.R")
```

## Calculate TAD in the model

mrgsolve will automatically calculate time after dose (`TAD`) for 
you and include it in the simulated output.

```{r}
doses <- ev(amt = 100, ii = 6, addl = 3)

mod <- modlib("pk1")

mrgsim(mod, doses, tad = TRUE)
```

This works well when you need `tad` in the output; but what if you'd 
like to know `tad` while the model is running. For this case, use the 
`tad` plugin.

## Simple approach

The `self` object has a `.tad()` method that will give you the time 
since last dose into any compartment. 

```{c, eval = FALSE, filename = "model/tad-1.solv", code = readLines("model/tad-1.solv")}

```

This is easy and works well if there is dosing into just one compartment.

```{r}
mod <- mread("model/tad-1.solv")

doses <- ev(amt = 100, ii = 6, addl = 3)

out <- mrgsim(mod, doses, end = 48, delta = 1)

head(out, 12)

plot(out)
```



## More customized approach

You can also use the `tad` plugin to calcuate `tad` for multiple 
different dosing compartments.

In the model, we initialize a `tadose` object in `[ error ]` using the 
static keyword. You can take this approach if you will only need to work
with `tad` in `[ error ]`. Otherwise, you can construct the object in 
`[ global ]`. The argument to the constructor is the compartment number
for doses you want to track.

Then call `obj.tad(self)` to get the current time after the most recent
dose for the monitored compartment. 

```{c, eval = FALSE, filename = "model/tad-2.solv", code = readLines("model/tad-2.solv")}

```

Note that you _have_ to call `obj.tad(self)` on every record so the 
object can know when the doses are happening.

```{r}
mod <- mread("model/tad-2.solv")

doses <- ev(amt = 100, ii = 6, addl = 3)

out <- mrgsim(mod, doses, end = 48, delta = 1)

head(out, 12)

plot(out)
```


